---
title: "Dose Finding with Multiple Toxicities using CRM"
author: "Group 3: Laura Cosgrove, Yue Gu, Jianyou Liu, Jingwei Ren, Kee-Young Shin, Chu Yu, Adina Zhang"
date: "10/21/2019"
output: 
  slidy_presentation:
    duration: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(kableExtra)
library(data.table)
```

## Prompt

- What are the design parameters? 
- What are performance metrics?
- Which dose will you start the trial at?

\newline
\newline
\newline

```{r}
table = tibble(" " = c("2.5 mg/100 ml","5.0 mg/100 ml"),

               "0 mg/100 ml" = c("X", ""),

               "66 mg/100 ml"= c("X","X"),

               "80 mg/100 ml" = c("", "X"),

               "100 mg/100 ml" = c("", "X"))

table %>% knitr::kable() %>%

kable_styling(latex_options = c("striped")) %>%

add_header_above(c("Cabazitaxel" = 1, "Cisplatin dose" = 4))
```

## Multiple toxicity levels: how to model

One approach: 

  - Weighted combination of toxicity outcomes proportionate to seriousness of event = Total toxicity burden (TTB) (Bekele and Thall, 2004)
    - Some problems: Total toxicity burden is not that interpretable (compared to setting separate limits for each grade of outcome)
    - Not for this problem, but for others, the modelled distribution can get high-dimensional if there are many types of toxicity.
    
## Multiple toxicity levels: how to model

Alternate approach (Lee et al., 2011): define the MTD using Continual Reassessment Method (CRM) with respect to multiple toxicity contraints set on separate toxicity grades:

$$MTD = \theta = argmax\{Pr(T \ge t_{l}|x) \le p_l, \ l = 1, ... L\}$$

- T are toxicity grades 
- $l$ = 1...L are the prespecified toxicity constraints in terms of T.
- $t_1 < ... < t_L$ are prespecified toxicity thresholds
- $p_1 > ... > p_L$ are their respective target probabilities

## Model, continued

To identify the model, define a  latent normally-distributed variable Z with:
  
  $$EZ = \alpha + \beta x, \ Var(Z) = 1$$ 
  
Such that:

$$t_l \le T \le t_{l+1} \ \ iff \ \ \gamma_l \le Z \le \gamma_{l+1}$$
 
In this way, it's not necessary to directly model the distribution T within each interval $[t_l, t_{l+1}]$, while still allowing ourselves to identify the distribution:
    
$$Pr(t_l \le T \le t_{l+1}|x) = Pr(\gamma_l \le Z \le \gamma_{l+1} | x)$$ 

$$Pr(t_l \le T \le t_{l+1}|x) = Pr(Z \le \gamma_{l+1} | x) - Pr(Z \le \gamma_{l} | x)$$ 
$$= Pr({Z - EZ}\le \gamma_{l+1} - (\alpha + \beta x)  | x) - Pr({Z - EZ} \le \gamma_{l} - (\alpha + \beta x) | x)$$ 
$$= \Phi(\gamma_{l+1} - (\alpha + \beta x)) - \Phi(\gamma_{l} - (\alpha + \beta x))$$ 
$$Pr(T \le t_{l+1}|x) - Pr(T \le t_{l} | x) = \Phi(\gamma_{l+1} - (\alpha + \beta x)) - \Phi(\gamma_{l} - (\alpha + \beta x))$$ 

## Model result

  - Since $t_0 \equiv 0$:
  
  $$-1*Pr(T \le t_{l} | x) =  -1*\Phi(\gamma_{l} - (\alpha + \beta x))$$
  
$$Pr(T \ge t_{l} | x) =  \Phi(\alpha + \beta x - \gamma_{l})$$
  
Note our objective:

$$MTD = \theta = argmax\{Pr(T \ge t_{l}|x) \le p_l, \ l = 1, ... L\}$$
$$\theta = argmax\{\Phi(\alpha + \beta x - \gamma_{l})\le p_l\, \ l = 1, ... L\}$$

## Design Parameters

For modelling:

- Take $\alpha = 3$ (convention, Cheung 2002).
  
- Objective can be written as  $\theta = min\{\theta_1, ..., \theta_L\} = \theta_{\lambda}$, where each toxicity constraint is met at the respective dose levels:
  -  Note that the inverse normal CDF is the probit

  
$$\theta_l = \frac{{\gamma_l + \Phi^{−1}(p_l) − 3}}{\beta}$$
  
- So given two toxicity grades (L = 2), we need to estimate is an explicit function of our design parameters: $\gamma_1, \gamma_2, p_1, p_2, \beta$

- Specify prior distributions for  $\gamma_1, \gamma_2, \beta$ $\sim exp(1)$

- Specify a halfwidth $\delta$ for the indifference interval 

- Specify target DLT rates for grade 2 and 3 toxicity, $p_1, p_2$ and choose skeleton for each toxicity level: $(p_{0,1, 1}.  p_{0,2,1}, p_{0,3,1}, p_{0,4,1},  p_{0,5.1})$ and $(p_{0,1,2},  p_{0,2,2}, p_{0,3,2}, p_{0,4,2},  p_{0,5,2})$ 


## Performance metrics

- Estimated probability of correct selection 

- Average probability of dose selection for all doses

- Patient allocation: proportion of patients treated at each level

- Mean, median and interquartile range (IQR) for the estimated probability of DLT, grade level 2

- Mean, median and interquartile range (IQR) for the estimated probability of DLT, grade level 1

## Choosing Starting Dose

- "Since $\theta = min\{\theta_1, ..., \theta_L\} \le \theta_1$, it is reasonable to believe that a prior guess of MTD should be somewhere below $d_v$. In light of this, we call a starting dose $x_1$ permissible if $x_1 \le d_v$." (Lee et al., 2011)

- In this problem, L = 2 and the prior MTDs $d_v$ is for L = 2 for each product.

- Further, the two $d_v$ are for the component, not combination, products.

- This suggests we should start the dose finding at a lower dose

- Choose the lowest dose

## Assigning Doses #1
1. Randomization: randomized patients into 2 groups based on Cabazitaxel dose level(2.5 or 5.0 mg/100ml)
```{r}
rbind(c("(1,1)","(1,2)","(1,3)","(1,4)"),
      c("(2,1)","(2,2)","(2,3)","(2,4)")) %>% 
  as.data.frame() %>% 
  setattr("row.names", c("2.5mg/100ml", "5.0mg/100ml")) %>%
  setnames(c("0", "66", "80", "100")) %>% 
  knitr::kable(row.names = T)
  
```


## Assigning Doses #2
2. Choosing starting dose: apply $L_1$=(1,1) to group 1 patients (2.5mg/100ml)
3. Apply $CRM-MC_2$: "define $\tilde{\theta}=\hat{\theta}_{n,\hat{\lambda_n}}$, where $\hat{\theta}_{n,l}$ denotes the marginal posterior median of $\theta_l$ given the first n obs, and $\hat{\lambda}_n=argmin_l\hat{\theta}_{n,l}$. The next patient is given $\tilde{x}_{n+1}=argmin_{d_k}|d_k-\tilde{\theta}_n|$" (Lee et al., 2011)
4. Trial: start the trial to get dose level chart and dose-toxicity curve
5. Choosing start dose $L_2=(2,1)$ to group 2 patients (5.0mg/100ml) and redo steps following step3 and step4
6. Compare the dose-toxicity curve from group 1 and 2, decide the recommended MTD (with target p)